% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Salman Shah}
    \newcommand{\CVTitle}{Salman Shah's Resume }
\newcommand{\CVNote}{CV compiled on {\today}}
\newcommand{\CVWebpage}{http://salman-bhai.github.io/My-Website/}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{https://www.google.co.in/maps/search/3rd+Block,+National+Institute+of+Technology,+Dodda+Kopla,+Surathkal,+Karnataka+575025/@13.0125878,74.798059,15z/data=!3m1!4b1}
{Room 53, Boys Block 3, NITK Hostels, Srinivasnagar, Surathkal, Mangalore - 575025}
\par
\href{mailto:sbs.191197@gmail.com}
{sbs.191197@gmail.com}
\,\SubBulletSymbol\,
+91\,886\,189-7183
\,\SubBulletSymbol\,
\textcolor{blue}{\href{\CVWebpage}
{\url{\CVWebpage}}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\textcolor{blue}{
\href{http://nitk.ac.in/}
{\textbf{NITK Surathkal}}
}
,Surathkal, Mangalore, India
\hfill
\DatestampYMD{2015}{08}{23} --
\DatestampYMD{2019}{04}{23}
(Expected)

\Gap
\BulletItem
B. Tech. in 
\textcolor{blue}{
\href{http://infotech.nitk.ac.in/}
{Information Technology}
}
\Gap

\Entry
\textcolor{blue}{
\href{http://www.iitianspace.com/}
{\textbf{IITians PACE Junior Science College}}
}
\hfill
\DatestampYMD{2013}{06}{15} --
\DatestampYMD{2015}{06}{15}
\Gap

\BulletItem
89.85\% in 
\href{https://drive.google.com/open?id=0BxuVe1f_hNs2TDA4em5UUE9jdDQ}
{HSC Board Examination}
\Gap

\BulletItem
All India Rank 2214 in 
\href{http://www.example.com/my-department}
{JEE (Mains) Entrance Examination}
\Gap

\Entry
\textcolor{blue}{
\href{http://www.hansrajeducation.org/}
{\textbf{Hansraj Morarji Public School}}}
, Andheri(West), Mumbai, India
\hfill
\DatestampYMD{2008}{06}{23} --
\DatestampYMD{2013}{03}{15}

\Gap
\BulletItem
92.18\% in
\href{https://drive.google.com/file/d/0BxuVe1f_hNs2QXVwX2F2V0VXTEE/view?usp=sharing}
{SSC Board Examination}
\begin{Detail}
\end{Detail}

%%%%%%%%%%%%%%%%
%% EXPERIENCE %%
%%%%%%%%%%%%%%%%

\Section
{Experience}
{Experience}
{PDF:Experience}

\SubSection
{Startups}
{Startups}
{PDF:Startups}

\Entry
\textbf{Lead Web and App Developer,}
\textcolor{blue}{
\href{http://wheelsonroll.com/}
{Wheels On Roll,}
}
Mangalore, India
\hfill
\DatestampYMD{2016}{09}{15} --
\DatestampYMD{2017}{03}{15}

\Gap
\BulletItem
Developed Static Website using HTML, CSS, JavaScript and open-source front-end frameworks like Materialize CSS as also using third-party APIs like Crisp to include Chat Functionality in the website.
\BulletItem
Worked with Product Development Team to develop an IoT framework using Sanic and Firebase to connect the hardware to the Mobile App. Also developed UI and UX of the Android app primarily using Google's Material Design Guidelines.
\Gap

\Entry
\textbf{Web and App Developer,}
\textcolor{blue}{
\href{http://changepay.in/}
{Change Pay,}
}
Mangalore, India
\hfill
\DatestampYMD{2016}{12}{15} --
\DatestampYMD{2017}{03}{15}

\Gap
\BulletItem
Developed Dynamic Website using HTML, CSS, JavaScript and front-end frameworks like Bootstrap using third-party APIs like Crisp to include Chat Functionality in the website.
\BulletItem
Developed User Sign In functionality in the website using Django framework thereby allowing users to check their balance online.
\BulletItem
Developed UI and UX of the Android app primarily using Google's Material Design Guidelines. Also worked with third-party APIs like PayUMoney to integrate a Payment Gateway inside the mobile app.

%%%%%%%%%%%%%%%%%%%%%%
%% TECHNICAL SKILLS %%
%%%%%%%%%%%%%%%%%%%%%%

\Section
{Technical Skills}
{Technical Skills}
{PDF:Technical Skills}

\Entry
\textbf{Languages/Markup and Scripts}
- C, C++, Java, Python, JavaScript, HTML, CSS, Bash.
\Gap

\textbf{Tools}
- Android Studio, NetBeans, Code::Blocks, PyCharm, vi Editor.
\Gap

\textbf{Frameworks}
- Git, STL, OpenGL, Jekyll, Materialize CSS, jQuery.
\Gap

\textbf{DBMS}
- Microsoft Azure, Firebase

\BigGap

%%%%%%%%%%%%%%%%%%%%%%%
%% SELECTED PROJECTS %%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Selected Projects}
{Selected Projects}
{PDF:SelectedProjects}

\Entry
All Projects available on
\textcolor{blue}{
\href{https://github.com/salman-bhai}
{\textbf{GitHub}}}

\Gap

\BulletItem
\textcolor{blue}{
\href{https://github.com/salman-bhai/NotesNearby}{
\textbf{Notes Nearby}}
}
Notes Nearby is an Augmented Reality based-app which takes Users' location to point to nearby restaurants and attractions. App is developed in Android using Microsoft Azure Database and Microsoft Cognitive Services for Speech-To-Text. 
\Gap

\BulletItem
\textcolor{blue}{
\href{https://github.com/Hrily/TopMusicPull}{
\textbf{Top Music Pull}}
}
Developed a Python Application to download top trending playlists like Billboard Top Hot 100, Vevo Top 20 from YouTube. Used Bash Scripting and Python for downloading the top-trending songs and used third-party libraries like Youtube-Dl for the same.    
\Gap

\BulletItem
\textcolor{blue}{
\href{https://github.com/salman-bhai/WhatsApp-Web}{
\textbf{WhatsApp Web}}
}
Developed a Terminal Interface to send messages via Computer Terminal to WhatsApp Web. Used Python Web Scraping to get the JavaScript from the Web. Developed only for Linux Computers and creates a local backup of upto 30 messages per user at a single instance.  
\Gap

\BulletItem
\textcolor{blue}{
\href{https://github.com/salman-bhai/My-Website}{
\textbf{Personal Website and Blog}}
}
Personal Website using Front End frameworks like MaterializeCSS and jQuery and Jekyll for 
\href{https://github.com/salman-bhai/Blog}{Blog} using Minima gem. Currently hosted on GitHub in line with Google's Material Design Guidelines.
\Gap

\BulletItem
\textcolor{blue}{
\href{https://github.com/salman-bhai/TicTacToe}{
\textbf{Tic Tac Toe}}
}
Built a Tic Tac Toe game implemented in Java and used Java Swing as GUI. 
Implemented User v/s User, User vs CPU (where CPU plays randomly), User vs AI and CPU vs AI (where AI implements Greedy Algorithm).
\Gap

\BulletItem
\textcolor{blue}{
\href{https://github.com/salman-bhai/NITKWebsite}{\textbf{NITK Website}}
}
Worked on the Front-end Website Team for NITK Website using HTML, CSS and JavaScript and front-end frameworks like Bootstrap, jQuery and Materialize CSS. 
{\textbf{(On Going)}}
\Gap

\BulletItem
\textcolor{blue}{
\href{https://github.com/IEEE-NITK/DeepNLP}{\textbf{Deep NLP}}
}
Deep Learning with NLP aims combines the power of Natural Language Processing with Deep Learning to train models using Google's Tesorflow Network to build a chatbot which answers questions given a sample corpus of Game of Thrones books and TV Series subtitles.
{\textbf{(On Going)}}
\Gap


\BulletItem
\textcolor{blue}{
\href{https://github.com/salman-bhai/stocks-predictor}{\textbf{Stockify}}
}
Stockify aims to combine the power of Machine Learning and Finance to create a custom Stocks Predictor which will predict the price of the stocks in a particular market. 
{\textbf{(On Going)}}
\Gap

\BigGap
%%%%%%%%%%%%%%%%%%%%%%
%% RELEVANT COURSES %%
%%%%%%%%%%%%%%%%%%%%%%

\Section
{Relevant Courses}
{Relevant Courses}
{PDF:Relevant Courses}

\Entry
Data Structures,
Digital Design and Computer Organization, Design and Analysis of Algorithms, Operating Systems, Networks, UNIX
Programming, Computer Graphics, Paradigms Of Programming - Part I and II, Object Oriented Analysis and Design, Probability, Graph Theory.

%%%%%%%%%%%%%%%%%%
%% ACHIEVEMENTS %%
%%%%%%%%%%%%%%%%%%

\Section
{Achievements}
{Achievements}
{PDF:Achievements}

\BulletItem
{\textbf{Winner (Microsoft Code.Fun.Do)}},
Online Round as well as Campus Round.
Created an Augmented Reality based app which determines locations via Maps API
and uses Azure Database.
\Gap

\BulletItem
{\textbf{Top 20 Repositories around the World:}}
Participated in HacktoberFest 2k16 and
had one repository featuring in the Top 20 Most Committed Repository around the
world.
\Gap


\BulletItem
{\textbf{Project Presentation: }}
Presented a research project at the 19th Indian National Children Science Congress on “Leafy Vegetables grown near Railway Tracks – Fit for Consumption or not”.
\Gap

\BulletItem
{\textbf{Scored 99.8 percentile }}
in the All-India entrance exam for NITs – JEE (Mains).\Gap

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% EXTRA CURRICULAR ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Extra Curricular Activites}
{Extra Curricular Activites}
{PDF:ExtraCurricularActivites}

\BulletItem
{\textbf{Executive Member}}
at IEEE-NITK Student Branch.
\Gap

\BulletItem
{\textbf{Editorial Team Member}}
at Team Shoreline(College Magazine).
\Gap

\BulletItem
{\textbf{Member}}
at LSD - Literary, Stage and Debating Society.
\Gap


\BulletItem
{\textbf{Competitive Programming: }}
Active on popular websites like
\textcolor{blue}{
\href{https://www.codechef.com/users/sbshah}{Codechef}} and 
\textcolor{blue}{
\href{https://www.hackerrank.com/SalmanBhai}{HackerRank}}.

\Gap

\end{Body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\UseNoteFont%
\null\hfill%
[\textit{\CVNote}]

\end{document}
